\textbf{Integrating spatial and temporal patterns \\ in ecological forecasts }

### 2018-07-02 doc/manuscript.tex
Writing up community example, starting Appendix B

\usepackage{amsmath,amsfonts,amssymb,graphicx,setspace,authblk}
\usepackage{float}
\usepackage[running]{lineno}
\usepackage[vmargin=1in,hmargin=1in]{geometry}

@@

\title{\textbf{Integrating spatial and temporal patterns in ecological forecasts }}

@@

\section*{Description of the eco-evolutionary annual plant model}

@@

\section*{Estimating model weights}

@@

>>>>

\usepackage{amsmath,amsfonts,amssymb,graphicx,setspace,authblk}
\usepackage{float}
\usepackage[running]{lineno}
\usepackage[vmargin=1in,hmargin=1in]{geometry}
\usepackage[sc]{mathpazo} %Like Palatino with extensive math support

@@

\title{\textbf{Integrating spatial and temporal patterns \\ in ecological forecasts }}

@@

\section{Description of the eco-evolutionary annual plant model}

@@

\subsection{Estimating model weights}

@@

\section{Description of the metacommunity model}

[How much detail to include from Alexander et al?]

-Describe spatial model

-Describe temporal model

-Model weights
